### 2021-07-06 rad-icfp-2021/purerad.tex
typo

Finally, we add two new shift operator !shift1L, shift1R!. 
They take an array of size $n$, and shift respectively forget the first and the last element of the array.
These somewhat ad-hoc operators naturally show up when differentiating fold-like operators.

The types and terms are presented in Figure~\ref{fig:target_grammar}.
Our lambda abstractions take $n$ arguments as we are not interested here with partial applications. 
In fact, the lambda abstractions introduced by reverse-mode will be removed during partial evaluation 
and the notation with lambda abstractions having $n$ bound variables makes reading slightly easier.
We note that we don't actually need the full power of higher-order because we only use lambda abstractions over variables of ground types
and let expressions binding such lambda abstractions. So we only require the target language to be second-order.
The type system for the extended grammar of the target language is presented in Figure~\ref{fig:target_typesystem}.

>>>>

Finally, we add two new shift operator !shift1L!, !shift1R!. 
They take an array of size $n$, and respectively forget the first and the last element of the array.
These somewhat ad-hoc operators naturally show up when differentiating fold-like operators.

The types and terms are presented in Figure~\ref{fig:target_grammar}.
Our lambda abstractions take $n$ arguments as we are not interested here with partial applications. 
In fact, the lambda abstractions introduced by reverse-mode will be removed during partial evaluation 
and the notation with lambda abstractions having $n$ bound variables makes reading slightly easier.
We note that we don't actually need the full power of higher-order because we only use lambda abstractions over variables of ground types
and let expressions binding such lambda abstractions. We only need the target language to be second-order.
The type system for the extended grammar of the target language is presented in Figure~\ref{fig:target_typesystem}.
